---
name: Xiaotao
surname: Shen
profilepic: xiaotaoshen.jpg
address: "3165 Porter Dr, Palo Alto, CA 94304"
position: "Postdoctoral Researcher Stanford University"
phone: +1 571 267 9283
website: "jaspershen.github.io"
email: "shenxt@stanford.edu"
twitter: "xiaotaoshen1990"
github: "jaspershen"
linkedin: "shenxt"
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "e3142c"
output: 
  vitae::moderncv:
    theme: classic
    keep_tex: true
header-includes:
   - \usepackage{times}
   - \renewcommand{\normalsize}{\fontsize{11}{12}\selectfont}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Research Interests

* Mass Spectrometry Data Processing Algorithms and Software Development
* Multi-omics Data Integration Methods Development
* Wearable Data and Precision Medicine
* Aging and Neurodegenerative Diseases
* Human Pregnancy-Related Disease Diagnosis and Mechanism Research
* Environmental Health

# Education & Research Experiences

```{r}
library(tibble)
tibble::tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Postdoctoral Research Fellow", "2019/04-Present", "Stanford University", "Palo Alto, USA",
  "Ph.D.", "2013/09-2018/12", "University of Chinese Academy of Sciences", "Shanghai, China",
  "B.S.", "2009/09-2013/07", "Inner Mongolia University", "Hohhot, China",
) %>% 
  vitae::detailed_entries(Degree, Year, Institution, Where)
```

# Honors & Awards

```{r}
tibble::tribble(
  ~Year, ~Type, ~Desc,
  2023, "Young Investigator Award", "The 3rd Chinese American Society For Mass Spectrometry Conference",
  2023, "SPORR 2023 Rigor and Reproducibility Award", "Stanford Program on Research Rigor and Reproducibility",
  2021, "Winner Selected by the Event Committee", "Exposome Data Challenge Event",
  2018, "Student Travel Award for Oral Presentation", "The International Metabolomics Society",
  2018, "International Conference Travel Award", "The Metabolites Journal",
  2017, "China National Scholarship", "Ministry of Education of the People’s Republic of China",
  2017, "Award for Outstanding Youth Report", "The 3rd China MS Analysis Conference",
  2016, "Merit Student", "University of Chinese Academy of Sciences",
  2016, "Award for Outstanding Youth Report", "The 34th China MS Society Conference",
  2013, "Inner Mongolia Outstanding Graduate", "Inner Mongolia Autonomous Region",
  2011, "National Encouragement Scholarship", "Inner Mongolia University"
) %>% 
  vitae::brief_entries(
    Type,
    Year, 
    Desc
  )
```

# Presentations

## Oral Presentations------------------------------------------------

```{r}
tibble::tribble(
  ~ title, ~ event, ~ where, ~ year,
  "Nonlinear Dynamic Changes During Human Aging Revealed in Multi-omics Profiles", "Bay Area Metabolism Meeting (BAMM) 2023", "Palo Alto, USA", "2023/09",
    "Multi-omics Microsampling for The Profiling of Lifestyle-Associate Changes in Health", "The 3rd Chinese American Society for Mass Spectrometry Conference", "Virtual meeting", "2023/08",
  "Multi-omics Microsampling for The Profiling of Lifestyle-Associate Changes in Health", "The 71th American Society for Mass Spectrometry Conference", "Houston, USA", "2023/06", 
  "Remote and Flexible Microsampling Multi-omics for Precision Medicine", "iPOP summit", "Palo Alto, USA", "2023/04",
  "Bioinformatics Algorithm Development for Mass Spectrometry Data and its Application to Precision Medicine. Invited presentation", "Altos Labs", "Redwood City, USA", "2023/03",
"Multi-omics Microsampling for The Profiling of Lifestyle-Associate Changes in Health", "Invited presentation", "Wuhan, China", "2023/02",
"Multi-omics Microsampling for The Profiling of Lifestyle-Associate Changes in Health", "Stanford Postdoc Symposium", "Palo Alto, USA", "2023/02",
"Bioinformatics Method Development for Mass Spectrometry and its Application to Precision Medicine", "Stanford CVI Early Career Research Roundtable", "Palo Alto, USA", "2022/11",
"Deep Learning-based Pseudo-Mass Spectrometry Imaging Analysis for Precision Medicine", "CASMS Virtual Conference", "Virtual meeting", "2022/10",
"TidyMass: An Object-oriented Reproducible Analysis Framework for LC-MS Data", "ACS Fall 2022", "Virtual meeting", "2022/08",
"metID: an R Package for Automatable Compound Annotation for LC-MS-based Data", "The 69th American Society for Mass Spectrometry Conference", "Philadelphia, USA", "2021/11",
"Decoding Links Between the Exposome and Health Outcomes by Multi-omics Analysis", "Exposome Data Challenge Event", "Virtual meeting", "2021/04",
"Metabolic Reaction Network-based Recursive Metabolite Identification for Untargeted Metabolomics", "The 14th International Conference of the Metabolomics Society", "Seattle, USA", "2018/06",
"Assessment of the Response to Neoadjuvant Chemo-Radiation in Rectal Cancer Patients based on a Metabolomics Approach", "The 3rd China Mass Spectrometry Analysis Conference", "Xiamen, China", "2017/12",
"Normalization and Integration of Large-Scale Mass Spectrometry-based Metabolomics Data Using Support Vector Regression", "The 34th China Mass Spectrometry Society Conference", "Xining, China", "2016/09",
"Normalization and Integration of Large-Scale MS-based Metabolomics Data Using Support Vector Regression", "The 64th American Society for Mass Spectrometry Conference", "San Antonio, USA", "2016/06"
) %>%
  vitae::detailed_entries(what = title, 
                       when = year, 
                       with = event, 
                       where = where)
```

## Poster Presentations------------------------------------------------

```{r}
tibble::tribble(
  ~ title, ~ event,  ~ year, ~ where,
"Nonlinear Dynamic Changes During Human Aging Revealed in Multi-omics Profiles", "Stanford Bio-X Interdisciplinary Initiatives Seed Grants Program Symposium 2023", "2023/09", "Stanford, USA", 
"TidyMass: An Object-oriented Reproducible Analysis Framework for LC-MS Data", "Stanford Data Science Conference", "2023/05", "Palo Alto, USA", 
"Deep Learning-based Pseudo-Mass Spectrometry Imaging Analysis for Precision Medicine", "Stanford Genetics Retreat 2022", "2022/09", "Monterey, USA",
"Deep Learning-based Pseudo-Mass Spectrometry Imaging Analysis for Precision Medicine", "Bay Area Metabolism Meeting (BAMM) 2022", "2022/09", "Palo Alto, USA",
"TidyMass An Object-oriented Reproducible Analysis Framework for LC-MS Data", "The 70th American Society for Mass Spectrometry Conference", "2022/06", "Minneapolis, USA",
"Longitudinal Interactions Between Levels of Serum Cytokine and the Microbiome from Four Body Sites", "IMMUNOLOGY2022", "2022/05", "Portland, USA",
"TidyMass: An Object-oriented Reproducible Analysis Framework for LC-MS Data", "Stanford Genetics Retreat 2021", "2021/09", "Palo Alto, USA",
"Longitudinal Urine Metabolic Profiling and Gestational Age Prediction in Pregnancy", "The 17th International Conference of the Metabolomics Society", "2020/06", "Virtual meeting",
"Metabolic Reaction Network based Metabolite Annotation in Untargeted Metabolomics", "The 13th International Conference of the Metabolomics Society", "2017/06", "Brisbane, Austria" 

) %>%
  vitae::detailed_entries(what = title, 
                       when = year, 
                       with = event, 
                       where = where)
```


# Teaching Experiences

```{r}
library(tibble)
tibble::tribble(
  ~ Year, ~ Class, ~ Institution,
  "2022/09", "LC-MS Data Processing and Analysis Using R language", "Biotree Company",
  "2022/03", "R Language for Reproducible Data Analysis", "SCPA",
  "2019/08-Present", "Stanford School of Medicine Intern", "Stanford University",
  "2014/09-2014/12", "Chinese Academy of Sciences", "Mass Spectrometry Analysis"
) %>% 
  vitae::brief_entries(what = Class, 
                       when = Year, 
                       with = Institution)
```

# Journal Referee

•	Nature Biotechnology
•	Nature Communications
•	Briefing in Bioinformatics
•	Bioinformatics
•	GigaScience
•	PLOS one
•	Phytochemistry
•	Genomics, Proteomics&Bioinformatics
•	Communications Chemistry
•	Communications Biology
•	Frontiers Molecular Biosciences
•	iMeta
•	Proteomics

# Volunteering

```{r}
library(tibble)
tibble::tribble(
  ~ Year, ~ Title, ~ Institution,
  "2023/08-Present", "Member of Editorial Board", "pj Women’s Health",
  "2023/02-Present", "Member of Youth Editorial Board", "Phenomics",
  "2023/01-Present", "Member of Youth Editorial Board", "Brain-X",
  "2022/07-Present", "Member of Youth Editorial Board", "iMeta",
  "2021/07-2022/07", "Co-Chair", "Stanford Chinese Postdoctoral Association",
  "2020/01-2021/12", "Organizer", "Stanford Chinese Postdoctoral Oral Presentation Improvement",
  "2019/04-2022/07", "Member", "Stanford Chinese Postdoctoral Association"
) %>% 
  vitae::brief_entries(what = Title, 
                       when = Year, 
                       with = Institution)
```


# Patents

```{r}
library(dplyr)
vitae::bibliography_entries("patents.bib") %>% 
  arrange(desc(issued))
```


# Publications

## First/Co-first Author Publications------------------------------------------------

```{r}
library(dplyr)
# knitr::write_bib(c("vitae", "tibble"), "my_publications.bib")

vitae::bibliography_entries("first_author.bib") %>% 
  arrange(desc(issued))
```

## Collaborative Publications------------------------------------------------

```{r}
library(dplyr)
vitae::bibliography_entries("collaborative_publications.bib") %>% 
  arrange(desc(issued))
```

## Submitted Publications------------------------------------------------

```{r}
library(dplyr)
vitae::bibliography_entries("submitted.bib") %>% 
  arrange(desc(issued))
```


